Dual terminal sliding mode control

### 2016-05-16 paper3_manuscript.tex
20160516

\section{Dual sliding mode control}
Consider a four-order nominal nonlinear system:

@@

\dot x_5(t) &= f_2(\bm x,t)+g_2(\bm x,t)+b_2(\bm x,t)u_2(t),\label{eq:four order system}

@@

For stabilization of the four-order system shown as~Eq. (\ref{eq:four order system}), dual sliding mode control inputs can be given according the following theorem.

@@

The four-order system (\ref{eq:four order system}) will reach the desired manifold $\bm s = 0$ shown in~Eq. (\ref{eq:dual sliding manifold}) in finite time. The states of the system will converge to zero along the manifold $\bm s=0$ in finite time, if the inputs are designed as follows:

@@

Hence, the system (\ref{eq:four order system}) asymptotically converges to the desired manifold (\ref{eq:dual sliding manifold}), and incidentally the convergent time can be calculated according to the finite time convergence theory.\par
Once the system (\ref{eq:four order system}) reaches the desired manifold~(\ref{eq:dual sliding manifold}), the whole system is handled by the reduced system:

@@

On the basis of Theorem \ref{theorem:1}, we can develop the parameters in the manifold to improve the performance, which introduces a modified method for stabilizing the system~(\ref{eq:four order system}), and furthermore this method makes the design of the manifold more flexible. Considering the system~(\ref{eq:four order system}) with the manifold manifold $\bm s = [s_1,s_2]^T$, the details of which can be described by following expressions:

@@

The four-order system (\ref{eq:four order system}) will reach the desired manifold $\bm s = 0$ shown in~Eq. (\ref{eq:modified dual sliding manifold}) in finite time. The states of the system will converge to zero along the manifold $\bm s=0$ in finite time, if the inputs are designed as follows:

@@

Considering the four-order system (\ref{eq:four order system}), the terminal sliding mode manifold can be designed as:

@@

Adopting the control scheme mentioned above, the system~(\ref{eq:four order system}) will converge to zero in finite time without any singularity occurring during the regulation process.

@@

Consider a four-order system (\ref{eq:four order system}), and for eliminating the singularity in inputs of the MDSM scheme, select a new inputs to complete the nonsingular MDSM scheme. Introducing the saturation terms into the original inputs yields:

@@

one can obtain a nonsingular solution to the stabilization of the system~(\ref{eq:four order system}), providing the finite time convergence by using sliding mode technique.

@@

\section{Dual sliding mode control for rigid manipulators}
In this section, a dual sliding mode control is proposed for the rigid $2$-link robot manipulator

@@

where $M_0(\bm q)$, $C_0(\bm q,\dot {\bm q})$ and $g_0(\bm q)$ are the estimated terms affected by the the uncertainties including $M_0(\bm q)$, $C_0(\bm q,\dot {\bm q})$, $g_0(\bm q)$, and the disturbance $\bm{d}(t)$. Particularly, the following assumption is exhibited to explain the bounded characteristics of the robot dynamics \cite{feng2002non}:

@@

&\Vert g(\bm q)\Vert< \psi_0+\psi_1\Vert\bm q\notag\Vert

@@

On the basis of the above results, one can design the dual sliding mode scheme for $2$-link robot manipulator by utilizing the following theorem.

@@

\bm u_2 &= -\frac{(\bm s^TM_0^{-1}(\bm q))^T}{\Vert\bm s^TM_0^{-1}(\bm q)\Vert}(\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2).

@@

in which it is assumed that the parameters $\mu_0$, $\mu_1$ and $\mu_2$ are known.

@@

At this point, the dual sliding mode control scheme for $2$-link robot manipulator has been demonstrated, and this technique is able to be extended to $n$-link manipulator. Consider a $n$-link robot manipulator in where $n$ is an even number, and the desired sliding manifold can be designed as

@@

The singularity of the DSM scheme for the robot manipulator can be eliminated by using the technique introduced in Theorem \ref{theorem:3}.

@@

\section{Simulation studies}

@@

For verifying the effectiveness of the proposed control scheme, consider the following four-order nonlinear system with the disturbance:

@@

\dot x_4 &= 0.3\sin(3t)+0.5e^{-3t}+u_2,\label{eq:simulation four order system}

@@

and one can produce a MDSM control scheme conveniently. It is obvious that the disturbance in the system~(\ref{eq:simulation four order system}) behaves bounded, which is said to be the following uncertainty terms:

@@

and hence, based on the analysis in Theorem~\ref{theorem:1}, $\eta_1>0.1$ and $\eta_2>0.8$ can be determined accordingly to guarantee the reaching condition of the desired sliding manifold. Also, the inputs $u_1$ and $u_2$ are able to be viewed as virtual input terms which consist of the linear combination of the crucial inputs in system, i.e., for the system~(\ref{eq:simulation four order system}), the input terms can be expressed by $\bm u = \Xi\bm\tau$ particularly, where $\bm u\in R^2$ is the virtual input vector; $\bm \tau\in R^2$ stands for the crucial input vector; $\Xi\in R^{2\times 2}$ must have full rank.\par
The system is supposed to be conducted to the desired state $\bm x_d=(0,0,0,0)$ from a prescript state $\bm x_0=(1.2,1.2,1.2,1.2)$. Admittedly, this prescript condition leads to a lager initial approaching distance due to the existence of the cubic terms $\gamma x^3$ in the sliding manifold, therefore a large approaching speed $k_i$ is required correspondingly. The control parameters are chosen as: $\alpha = 0.6$, $\lambda = 0.5$, $\gamma = 3$ and $\eta = 20$. Besides the large approaching speed selected, $\gamma$ accelerates the sliding phase indirectly. Therefore the design of the MDSM controller for the system~(\ref{eq:simulation four order system}) is finished, and the corresponding simulation results are illustrated in Figure~\ref{Figure:2} and Figure~\ref{Figure:3}.\par

@@

At this point, some effectiveness of the MDSM control scheme proposed above has been verified, and in the next section, we will apply it to stabilize the behavior of a $2$-link robot manipulator directly.

@@

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig3.eps}
\caption{2}
\label{Figure:3}
\end{figure}
\subsection{Performance of the robot manipulator}
In order to evaluate the performance of the proposed control scheme, a simulation about the $2$-link robot manipulator is presented in the following context. Figure~\ref{Figure:1} is the $2$-link manipulator schematic, the dynamics of which can be explained by the dynamic equations in following forms:

@@

\begin{align}
\begin{bmatrix}
m_{12}(q_2) &m_{12}(q_2)\\
m_{21}(q_2) &m_{22}
\end{bmatrix}
\begin{pmatrix}
\ddot q_1\\
\ddot q_2
\end{pmatrix}
+
\begin{bmatrix}
-c(q_2)\dot q_1^2-2c(q_2)\dot q_1\dot q_2\\
c(q_2)\dot q_2^2
\end{bmatrix}+
\begin{bmatrix}
\xi_1(q_1,q_2) g\\
\xi_2(q_1,q_2) g
\end{bmatrix}=
\begin{pmatrix}
\tau_1\\
\tau_2
\end{pmatrix},
\end{align}
where
\begin{align*}
&m_{11}(q_2)=(m_1+m_2)r_1^2+m_2r_2^2+2m_2r_1r_2\cos(q_2)+J_1,\\
&m_{12}(q_2)=m_2r_2^2+m_2r_1r_2\cos(q_2),\\
&m_{21}(q_2)=m_{12}(q_2),\\
&m_{22}=m_2r_2^2+J_2,\\
&c(q_2)=m_2r_1r_2\sin(q_2),\\
&\xi_1(q_1,q_2) =(m_1+m_2)r_1\cos(q_2)+m_2r_2\cos(q_1+q_2),\\
&\xi_2(q_1,q_2) = m_2r_2\cos(q_1+q_2).
\end{align*}\par
The values of the parameters are listed here, $r_1=1m$, $r_2=0.8m$, $J_1=5 kgm$, $J_2=5kgm$, $m_1=0.5kg$, $m_2=1.5kg$. In this model, the uncertainty is brought in by estimated terms, namely, $\bar m_1=0.4$ and $\bar m_2=1.2$ which are all not the actuate value obviously. In addition, owing to that it sits on many terms in the dynamic equations, it's a severe challenge to guarantee the performance. Accordingly, the uncertainty parameters in Eq.~(\ref{eq:manipulator uncertainty}) are assumed to be $\mu_0=10$, $\mu_1=3$, $\mu_2=3$.\par
This section will give a set of simulation to examine the performance of the MDSM control in tracking the certain angle condition. The behavior of the manipulator should fulfill the initial and desired condition, namely, $(\bm q_0^T, \dot{\bm q}_0^T)= (0.3,0.2,0,0)$ and $({\bm q}_d^T,\dot{\bm q}_d^T)=(1,1,0,0)$. In order to ensure the stability and a fast convergent speed, the control parameters are chosen conservatively to make the manipulator track the desired attitude in finite time, and these parameters are $\alpha = 0.6$, $\gamma = 1$, $\lambda = 0.1$, $\eta = 100$. The terminal sliding mode control (TSM) scheme, as a comparison, is also implemented to regulate the behavior of the manipulator, the main control parameters of which are selected as $\alpha = 0.6$, $\gamma = 5$ and $\eta = 150$ to get a fairly good control performance.\par
The performance of the controllers mentioned above is illustrated in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}.
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig4.eps}
\caption{2}
\label{Figure:4}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig5.eps}
\caption{2}
\label{Figure:5}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig6.eps}
\caption{2}
\label{Figure:6}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig7.eps}
\caption{2}
\label{Figure:7}
\end{figure}
\section{Acknowledgment}
This work is partially supported by the National Natural Science Foundation of China (No. 61104112, 61503097).
\section{References}
\bibliography{paper3_ref}
\bibliographystyle{elsarticle-num}
\end{document}

>>>>

(...background of sliding mode control...)\par
(...sliding mode control develop...)\par
Recent years, the sliding mode control has become a popular solution to the issue about various control and signal process missions \cite{zhao2015nonlinear,zhang2015attitude}. Meza-S{\'a}nchez et al. applied the second sliding mode controller to a 3-DOF helicopter prototype, and verified the effectiveness via the experimental test bed \cite{meza2015output}. Zheng et al. implemented sliding mode control to eliminate the effect of the input quantization generated between the coder and the decoder \cite{zheng2016sliding}. Guzman et al. investigated the application of a sliding mode control in a power factor rectifier with constant switching frequency \cite{guzman2016sliding}. Said et al. designed a robust adaptive sliding mode method for a boost converter to guarantee the asymptotically stability \cite{oucheriah2013pwm}.  high order sliding mode control \cite{castillo2015higher,palosz2015laser}, super-twisting sliding mode\cite{zhao2015finite,liu2015second}
(...the terminal sliding mode develop...)\par
Normal linear hyperplane-based sliding mode control takes two steps to solve a problem about the stability, namely, conducting the system states onto the prescript sliding manifold and driving these states to the origin along the manifold. The first step is said to be the approaching phase which usually requires the states asymptotically or exponentially converge to the desired manifold, and the second step is the sliding phase which is related to the designed manifold closely. For achieving a fast convergence, the terminal sliding mode (TSM) control is developed based on the finite time control \cite{haimo1986finite,bhat1997finite,mu2016switching}, and comparing with the sliding mode control design mentioned above, the most significant contributions of the terminal sliding mode is introducing the finite time convergence to the sliding phase. Owing to the fast convergence, the terminal sliding mode control has been utilized to achieve the high precise control, i.e., in \cite{li2015robust}, an adaptive TSM scheme controlled a $2$-link robotic manipulator to track the variable signal. \par
In this paper, a dual sliding mode (DSM) controller is proposed for a class of two-order nonlinear systems with disturbances and uncertainties. A novel DSM manifold is exploited to fulfill the finite time convergence, and the approaching and sliding time are both able to be calculated directly. A modified DSM (MDSM) control scheme is presented to stabilize the motion of the $n$-link robotic manipulators. The remained paper is organized as follows: Section~\ref{sec:2} introduces a DSM scheme for a class of two-order system, and the finite time convergence of the approaching and sliding is verified. In addition, we add performance parameters for improving the DSM scheme to obtain the MDSM scheme, and the newly presented method has a better performance in theoretical analysis. In Section~\ref{sec:3}, the MDSM is applied to the motion regulation of the $n$-link robotic  manipulator, and the stability analysis is also carried out. Section~\ref{sec:4} exhibited the simulation results, and finally the conclusion is assigned in Section~\ref{sec:5}.
\section{Dual sliding mode control}\label{sec:2}
Consider a two-order nominal nonlinear system:

@@

\dot x_4(t) &= f_2(\bm x,t)+g_2(\bm x,t)+b_2(\bm x,t)u_2(t),\label{eq:two order system}

@@

For stabilization of the two-order system shown as~Eq. (\ref{eq:two order system}), dual sliding mode control inputs can be given according the following theorem.

@@

The two-order system (\ref{eq:two order system}) will reach the desired manifold $\bm s = 0$ shown in~Eq. (\ref{eq:dual sliding manifold}) in finite time. The states of the system will converge to zero along the manifold $\bm s=0$ in finite time, if the inputs are designed as follows:

@@

Hence, the system (\ref{eq:two order system}) asymptotically converges to the desired manifold (\ref{eq:dual sliding manifold}), and incidentally the convergent time can be calculated according to the finite time convergence theory.\par
Once the system (\ref{eq:two order system}) reaches the desired manifold~(\ref{eq:dual sliding manifold}), the whole system is handled by the reduced system:

@@

On the basis of Theorem \ref{theorem:1}, we can develop the parameters in the manifold to improve the performance, which introduces a modified method for stabilizing the system~(\ref{eq:two order system}), and furthermore this method makes the design of the manifold more flexible. Considering the system~(\ref{eq:two order system}) with the manifold manifold $\bm s = [s_1,s_2]^T$, the details of which can be described by following expressions:

@@

The two-order system (\ref{eq:two order system}) will reach the desired manifold $\bm s = 0$ shown in~Eq. (\ref{eq:modified dual sliding manifold}) in finite time. The states of the system will converge to zero along the manifold $\bm s=0$ in finite time, if the inputs are designed as follows:

@@

Considering the two-order system (\ref{eq:two order system}), the terminal sliding mode manifold can be designed as:

@@

Adopting the control scheme mentioned above, the system~(\ref{eq:two order system}) will converge to zero in finite time without any singularity occurring during the regulation process.

@@

Consider a two-order system (\ref{eq:two order system}), and for eliminating the singularity in inputs of the MDSM scheme, select a new inputs to complete the nonsingular MDSM scheme. Introducing the saturation terms into the original inputs yields:

@@

one can obtain a nonsingular solution to the stabilization of the system~(\ref{eq:two order system}), providing the finite time convergence by using sliding mode technique.

@@

\section{Dual sliding mode control for rigid manipulators}\label{sec:3}
In this section, a dual sliding mode control is proposed for the rigid $2$-link robotic manipulator

@@

where $M_0(\bm q)$, $C_0(\bm q,\dot {\bm q})$ and $g_0(\bm q)$ are the estimated terms affected by the the uncertainties including $M_0(\bm q)$, $C_0(\bm q,\dot {\bm q})$, $g_0(\bm q)$, and the disturbance $\bm{d}(t)$. Particularly, the following assumption is exhibited to explain the bounded characteristics of the robotic dynamics \cite{feng2002non}:

@@

&\Vert g(\bm q)\Vert< \psi_0+\psi_1\Vert\bm q\notag\Vert\\

@@

On the basis of the above results, one can design the dual sliding mode scheme for $2$-link robotic manipulator by utilizing the following theorem.

@@

\bm u_2 &= -k\frac{(\bm s^TM_0^{-1}(\bm q))^T}{\Vert\bm s^TM_0^{-1}(\bm q)\Vert}.

@@

in which $k>\mu_0+\mu_1\Vert\bm q\Vert+\mu_2\Vert\dot{\bm q}\Vert^2$, and it is assumed that the parameters $\mu_0$, $\mu_1$ and $\mu_2$ are known.

@@

At this point, the dual sliding mode control scheme for $2$-link robotic manipulator has been demonstrated, and this technique is able to be extended to $n$-link manipulator. Consider a $n$-link robotic manipulator in where $n$ is an even number, and the desired sliding manifold can be designed as

@@

The singularity of the DSM scheme for the robotic manipulator can be eliminated by using the technique introduced in Theorem \ref{theorem:3}.

@@

\section{Simulation studies}\label{sec:4}

@@

For verifying the effectiveness of the proposed control scheme, consider the following two-order nonlinear system with the disturbance:

@@

\dot x_4 &= 0.3\sin(3t)+0.5e^{-3t}+u_2,\label{eq:simulation two order system}

@@

and one can produce a MDSM control scheme conveniently. It is obvious that the disturbance in the system~(\ref{eq:simulation two order system}) behaves bounded, which is said to be the following uncertainty terms:

@@

and hence, based on the analysis in Theorem~\ref{theorem:1}, $l_1>0.1$ and $l_2>0.8$ can be determined accordingly to guarantee the reaching condition of the desired sliding manifold. Also, the inputs $u_1$ and $u_2$ are able to be viewed as virtual input terms which consist of the linear combination of the crucial inputs in system, i.e., for the system~(\ref{eq:simulation two order system}), the input terms can be expressed by $\bm u = \Xi\bm\tau$ particularly, where $\bm u\in R^2$ is the virtual input vector; $\bm \tau\in R^2$ stands for the crucial input vector; $\Xi\in R^{2\times 2}$ must have full rank.\par
The system is supposed to be conducted to the desired state $\bm x_d=(0,0,0,0)$ from a prescript state $\bm x_0=(1.2,1.2,1.2,1.2)$. Admittedly, this prescript condition leads to a lager initial approaching distance due to the existence of the cubic terms $\gamma x^3$ in the sliding manifold, therefore a large approaching speed $k_i$ is required correspondingly. The control parameters are chosen as: $\alpha = 0.6$, $\lambda = 0.5$, $\gamma = 3$ and $k = 20$. Besides the large approaching speed selected, $\gamma$ accelerates the sliding phase indirectly. Therefore the design of the MDSM controller for the system~(\ref{eq:simulation two order system}) is finished, and the corresponding simulation results are illustrated in Figure~\ref{Figure:2} and Figure~\ref{Figure:3}.\par

@@

At this point, some effectiveness of the MDSM control scheme proposed above has been verified, and in the next section, we will apply it to stabilize the behavior of a $2$-link robotic manipulator directly.

@@

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig3.eps}
\caption{2}
\label{Figure:3}
\end{figure}
\subsection{Performance of the robotic manipulator}
In order to evaluate the performance of the proposed control scheme, a simulation about the $2$-link robotic manipulator is presented in the following context. Figure~\ref{Figure:1} is the $2$-link manipulator schematic, the dynamics of which can be explained by the dynamic equations in following forms:

@@

\begin{align}
\begin{bmatrix}
m_{12}(q_2) &m_{12}(q_2)\\
m_{21}(q_2) &m_{22}
\end{bmatrix}
\begin{pmatrix}
\ddot q_1\\
\ddot q_2
\end{pmatrix}
+
\begin{bmatrix}
-c(q_2)\dot q_1^2-2c(q_2)\dot q_1\dot q_2\\
c(q_2)\dot q_2^2
\end{bmatrix}+
\begin{bmatrix}
\xi_1(q_1,q_2) g\\
\xi_2(q_1,q_2) g
\end{bmatrix}=
\begin{pmatrix}
\tau_1\\
\tau_2
\end{pmatrix},
\end{align}
where
\begin{align*}
&m_{11}(q_2)=(m_1+m_2)r_1^2+m_2r_2^2+2m_2r_1r_2\cos(q_2)+J_1,\\
&m_{12}(q_2)=m_2r_2^2+m_2r_1r_2\cos(q_2),\\
&m_{21}(q_2)=m_{12}(q_2),\\
&m_{22}=m_2r_2^2+J_2,\\
&c(q_2)=m_2r_1r_2\sin(q_2),\\
&\xi_1(q_1,q_2) =(m_1+m_2)r_1\cos(q_2)+m_2r_2\cos(q_1+q_2),\\
&\xi_2(q_1,q_2) = m_2r_2\cos(q_1+q_2).
\end{align*}\par
The values of the parameters are listed here, $r_1=1m$, $r_2=0.8m$, $J_1=5 kgm$, $J_2=5kgm$, $m_1=0.5kg$, $m_2=1.5kg$. In this model, the uncertainty is brought in by estimated terms, namely, $\bar m_1=0.4$ and $\bar m_2=1.2$ which are all not the actuate value obviously. In addition, owing to that it sits on many terms in the dynamic equations, it's a severe challenge to guarantee the performance. Accordingly, the uncertainty parameters in Eq.~(\ref{eq:manipulator uncertainty}) are assumed to be $\mu_0=10$, $\mu_1=3$, $\mu_2=3$.\par
This section will give a set of simulation to examine the performance of the MDSM control in tracking the certain angle condition. The behavior of the manipulator should fulfill the initial and desired condition, namely, $(\bm q_0^T, \dot{\bm q}_0^T)= (0.3,0.2,0,0)$ and $({\bm q}_d^T,\dot{\bm q}_d^T)=(1,1,0,0)$. In order to ensure the stability and a fast convergent speed, the control parameters are chosen conservatively to make the manipulator track the desired attitude in finite time, and these parameters are $\alpha = 0.6$, $\gamma = 1$, $\lambda = 0.1$, $k = 100$. The terminal sliding mode control (TSM) scheme, as a comparison, is also implemented to regulate the behavior of the manipulator:
\begin{align}
\begin{split}
\bm s &= \dot{\bm \varepsilon}+C_\gamma\lceil\bm{sgn}^\alpha(\bm \varepsilon)\rfloor\\
\bm\tau &= \bm u_0+\bm u_1 +\bm u_2\\
\bm u_0 &= -M_0(\bm q)C_r\lceil\alpha\vert\bm\varepsilon\vert^{\alpha-1}\dot{\bm \varepsilon}\rfloor\\
\bm u_1 &= M_0(\bm q)\ddot {\bm q}_d+C_0(\bm q,\dot {\bm q})+g_0(\bm q)\\
\bm u_2 &= -k\frac{(\bm s^TM_0^{-1}(\bm q))^T}{\Vert\bm s^TM_0^{-1}(\bm q)\Vert}.
\end{split}
\end{align}
where the main control parameters of which are selected as $\alpha = 0.6$, $\gamma = 5$ and $k = 150$ to get a fairly good control performance.\par
The performance of the controllers mentioned above is illustrated in Figure~\ref{Figure:4} and Figure~\ref{Figure:5}. Comparatively speaking, $q_1$ reaches the desired state at about $3s$ with the MDSM scheme, the reaching time of which is approximating $0.8s$ less than of the TSM scheme, and $q_2$ performs similar behaviors with a reasonable variable range of the angular rates. One can concentrate on the mission time of the entire motion, and inductively the time is decided by the manipulator finishing the final motion, i.e., for the manipulator controlled by utilizing the MDSM scheme, one can obtain the mission time $3s$ approximately, comparing with $3.25s$ for the TSM control. More notably, the control parameters of the TSM scheme have been optimally selected, whereas if using the parameters for the MDSM scheme, one can only get a fairy poor performance in the regulation, which leads to meaningless comparison. Therefore these results show that the MDSM control scheme can achieve the regulation of the manipulator effectively.
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig4.eps}
\caption{2}
\label{Figure:4}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig5.eps}
\caption{2}
\label{Figure:5}
\end{figure}
The more general case, the robotic manipulator is usually required to track variable signal, is discussed in this section. Particularly, one can continue to use the parameters of the controller mentioned above, and the mission condition is changed as follows:
\begin{align*}
&(\bm q_0^T, \dot{\bm q}_0^T)= (1.5,1.5,0,0)\\
&{\bm q}_d^T=(1.25-(1/5)e^{-t}+(1/20)e^{-4t},1.25+(9/40)e^{-t}-(1/4)e^{-2t})
\end{align*}\par
The simulation results are demonstrated in Figure~\ref{Figure:6} and Figure~\ref{Figure:7}, which plot the curves of states of the system~(\ref{eq:simulation two order system}) regulated by adopting the MDSM scheme. The control system completes the tracking mission at about $3.2s$ from a prescript initial condition, which performs a fairly small overshoot in the angle regulation.
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig6.eps}
\caption{2}
\label{Figure:6}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{paper3_fig7.eps}
\caption{2}
\label{Figure:7}
\end{figure}
\section{Conclusion}\label{sec:5}
A dual sliding mode control for n-link robotic manipulator has been presented. The method integrates two individual subsystem as a unity, then builds the manifold and input for it to complete the controller design. The control scheme can guarantee the reaching condition of the desired sliding manifold, meanwhile the system states can converge to the origin along the desired manifold. Also, the entire convergent time can be calculated accordingly. Developing the basic dual sliding mode yields the modified dual sliding mode control, providing a solution to eliminating chattering, avoiding singularity and fast convergence. For dealing with the under actuated characteristics which may appear in the system, the hierachical sliding mode technique will be considered to introduce into the control scheme, however, the control parameters selection is still a challenge.
\section{Acknowledgment}
This work is partially supported by the National Natural Science Foundation of China (No. 61104112, 61503097).
\section{References}
\bibliography{paper3_ref}
\bibliographystyle{elsarticle-num}
\end{document}
